|

### 2023-06-23 docs/resources.Rmd
Update to new repo name

---
title: "Resources on spatial models"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  A compliation of links to resources which I've found useful while working on `areal-comparison`.
---

>>>>

---
title: "Resources on spatial models"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  A compliation of links to resources which I've found useful while working on `beyond-borders`.
---

### 2023-06-23 src/1_checks/lengthscale-recovery.Rmd
Update to new repo name

#' l = 1
ck_one <- sim_ck(grid, nsim = 10, l = 1, save = FALSE)

@@

ggplot(df_lengthscale_one, aes(x = replicate, y = mean)) +
  geom_point() +
  geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
  geom_hline(yintercept = 1, size = 0.75, col = "grey", alpha = 0.75) +
  labs(x = "Replicate", y = "Posterior CrI", title = "Is l = 1 recovered?") +
  theme_minimal()

@@

ggplot(df_sigma_one, aes(x = replicate, y = mean)) +
  geom_point() +
  geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
  geom_hline(yintercept = 1, size = 0.75, col = "grey", alpha = 0.75) +
  labs(x = "Replicate", y = "Posterior CrI", title = "Is sigma = 1 recovered?") +
  theme_minimal()

plot(df_sigma_one$mean, df_lengthscale_one$mean)

@@

#' Contour plots of lengthscale and sigma

cbind(bind_rows(lengthscale_draws_one, .id = "replicate"), bind_rows(sigma_draws_one)) %>%
  rename("l" = "rstan::extract(fit)$l", "sigma_phi" = "rstan::extract(fit)$sigma_phi") %>%
  ggplot(aes(x = l, y = sigma_phi, col = as.factor(replicate))) +
  geom_density2d() +
  labs(x = "Length-scale",
       y = "Spatial random effect standard deviation",
       col = "Replicate",
       subtitle = "Tend to observe positive correlation in the samples") +
  theme_minimal()

@@

# ck_three <- sim_ck(grid, nsim = 30, l = 3, save = FALSE)
#
# fits_three <- lapply(ck_three, FUN = function(x) arealutils::ck_stan(x$sf))
# lengthscale_summary_three <- lapply(fits_three, FUN = function(fit) summary(fit)$summary["l", ])
# df_lengthscale_three <- list_to_df(lengthscale_summary_three)
#
# ggplot(df_lengthscale_three, aes(x = replicate, y = mean)) +
#   geom_point() +
#   geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
#   geom_hline(yintercept = 3, col = lightblue, size = 1.5)
#
# hist(df_lengthscale_three$mean - 3, breaks = 15)
# mean(df_lengthscale_three$mean - 3)

#' What does the prior look like, Gamma(1, 1)
ggplot(data = data.frame(x = c(0, 10)), aes(x)) +
  stat_function(fun = dgamma, n = 101, args = list(1, 1))

>>>>

#' l = 1
ck_one <- sim_ck(grid, nsim = 10, l = 1)

@@

ggplot(df_lengthscale_one, aes(x = replicate, y = mean)) +
  geom_point() +
  geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
  geom_hline(yintercept = 1, linewidth = 0.75, col = "grey", alpha = 0.75) +
  labs(x = "Replicate", y = "Posterior CrI", title = "Is l = 1 recovered?") +
  theme_minimal()

@@

ggplot(df_sigma_one, aes(x = replicate, y = mean)) +
  geom_point() +
  geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
  geom_hline(yintercept = 1, linewidth = 0.75, col = "grey", alpha = 0.75) +
  labs(x = "Replicate", y = "Posterior CrI", title = "Is sigma = 1 recovered?") +
  theme_minimal()

cor(df_sigma_one$mean, df_lengthscale_one$mean)

@@

#' Contour plots of lengthscale and sigma
cbind(bind_rows(lengthscale_draws_one, .id = "replicate"), bind_rows(sigma_draws_one)) %>%
  rename("l" = "rstan::extract(fit)$l", "sigma_phi" = "rstan::extract(fit)$sigma_phi") %>%
  ggplot(aes(x = l, y = sigma_phi, col = as.factor(replicate))) +
  geom_density2d() +
  labs(x = "Length-scale",
       y = "Spatial random effect standard deviation",
       col = "Replicate",
       subtitle = "Tend to observe positive correlation in the samples") +
  theme_minimal()

@@

# ck_three <- sim_ck(grid, nsim = 10, l = 3, save = FALSE)
#
# fits_three <- lapply(ck_three, FUN = function(x) arealutils::ck_stan(x$sf))
# lengthscale_summary_three <- lapply(fits_three, FUN = function(fit) summary(fit)$summary["l", ])
# df_lengthscale_three <- list_to_df(lengthscale_summary_three)
#
# ggplot(df_lengthscale_three, aes(x = replicate, y = mean)) +
#   geom_point() +
#   geom_errorbar(aes(ymin = X2.5., ymax = X97.5.)) +
#   geom_hline(yintercept = 3, col = lightblue, linewidth = 1.5)
#
# hist(df_lengthscale_three$mean - 3, breaks = 15)
# mean(df_lengthscale_three$mean - 3)

#' What does the prior look like, Gamma(1, 1)
ggplot(data = data.frame(x = c(0, 10)), aes(x)) +
  stat_function(fun = dgamma, n = 101, args = list(1, 1)) +
  theme_minimal()

### 2023-06-23 src/docs_paper/appendix.Rmd
Update to new repo name

---
title: Appendix to "Understanding models for spatial structure in small-area estimation"
author:
  - Adam Howes^[Department of Mathematics, Imperial College London]
  - Jeffrey W. Eaton^[Department of Epidemiology, Harvard University]
  - Seth R. Flaxman^[Department of Computer Science, Oxford University]
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: true
    includes:
      in_header: preamble.tex
bibliography: citations.bib
---

@@

# Comparison of AGHQ to other inference methods \label{app:aghq-nuts}

>>>>

---
title: |
  | Appendix to "Beyond borders: evaluating the suitability of spatial adjacency for small-area estimation"
author:
  - Adam Howes^[Department of Mathematics, Imperial College London]
  - Jeffrey W. Eaton^[Department of Epidemiology, Harvard University]
  - Seth R. Flaxman^[Department of Computer Science, Oxford University]
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: true
    includes:
      in_header: preamble.tex
bibliography: citations.bib
---

@@

# Comparison of AGHQ to NUTS \label{app:aghq-nuts}
